Vulnerability Analysis of Container Images in Neuroimaging

### 2020-07-05 paper.tex
worked on comments 1

@@

We scan a total of 44 container images taken from two containerization frameworks
used in neuroscience: BIDS
apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}.
Out of these 44 images, 26 were obtained from BIDS apps
\href{https://bids-apps.neuroimaging.io/apps/}{(https://bids-apps.neuroimaging.io/apps/)} 
and 18 from Boutiques. In fact, at the time of the study, BIDS apps had 27 images,
out of which one wasn't available on DockerHub. Boutiques had 49 images, listed using
Boutiques \texttt{bosh search} command,
however, only 23 unique images were listed, out of which 3 couldn't be retrieved and 2
 were already included in BIDS apps. All the final 26 images
from BIDS apps are Docker images, whereas Boutiques contains 18 Docker images
and 6 Singularity images.

@@

Anchore is an end-to-end, open-source container security platform. It
analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
In our experiments, we use Anchore Engine version 0.5.0 through Docker image \todo{insert name}, and
Anchore vulnerability database version 0.0.11.

Anchore compares package versions, which are present inside the
image, with the vulnerability database in order to flag vulnerabilities.
To get a vulnerability feed of various OS distributions, Anchore refers to
different sources, for instance, Ubuntu launchpad database to get
vulnerability data related to Ubuntu \tristan{You need to be accurate on these sources, this is not ``for instance". 
You should list all the sources used in the experiments, for all image types: Ubuntu but also CentOS, Debian, Alpine.}.

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD. It
offers both static and dynamic scanning, and both local and remote
scanning. In our experiments, we use remote dynamic scanning, that is, Vuls
starts a container for every image to test, and queries the package manager
in the image through SSH. We use Vuls 0.9.0, executed through Docker image
\todo{add Docker image name}. Vuls gets data from the Open Vulnerability
and Assessment Language (OVAL) database \tristan{Does it contain
vulnerabilities for all distributions?} \tristan{The Vuls website says that it uses multiple vulnerability databases: https://vuls.io/docs/en/main-features.html Are you sure 
that you only used OVAL and if so, why?}. It is worth noting that there is
no OVAL data for Ubuntu 17.04 and 17.10 distributions, meaning that images
with these distributions cannot be scanned with Vuls.

@@

Clair (\url{https://github.com/quay/clair}) is an open-source and extensible
vulnerability scanner for Docker and appc container images, developed by
CoreOS (now Container Linux), a Linux distribution to deploy container
clusters. Clair has a client-server architecture, in which the server
maintains a database of vulnerabilities. We use Clair through Clair scanner
(\url{https://github.com/arminc/clair-scanner}), a tool to facilitate the testing
of container images against a local Clair server. Clair scanner scans the image,
prepares the list of vulnerabilities, compares that list against a
whitelist, and flags vulnerabilities that are not present in the whitelist
\tristan{What is this whitelist about, and which one did you use?}. Clair
scanner maintains a Docker image with the up-to-date Ubuntu CVE tracker
database, used for the analysis \tristan{Please mention the vulnerability sources for all distributions}.
 We use Clair-scanner version 2.0.6, executed through
Docker image \texttt{arminc/clair-local-scan:v2.0.6}. For the vulnerability
database, we use Docker image \texttt{arminc/clair-db:latest}, last
updated on 2019-09-18.

@@

Singularity Tools (Stools)
are an extension of Clair scanner for Singularity images. Stools
directly scan the image files in a local installation of the Clair
scanner, to circumvent the Docker-specific requirements in the Clair API.
In our experiments, we use Singularity Tools version 3.2.1  through Docker
image
\texttt{vanessa/stools-clair:v3.2.1}
and we follow the steps mentioned in
\href{https://github.com/singularityhub/stools}{Stools Github} to scan
Singularity images. \tristan{which docker images did you use for clair and clair database?}

@@

Ubuntu maintains its vulnerability database in the Ubuntu Launchpad or the Ubuntu CVE Tracker. For a given CVE, there is an entry for all ubuntu releases.
Ubuntu releases are listed with the package name
in which vulnerability exists and are entitled a status
(\href{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
encoded in the following form:
\newline \\
\noindent <release>\_<source-package>: <status> (<version/notes>) \\
\newline\\
For a given release, the status can be any one of the following:

@@

\subsection{Image Minimization Process}
We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
An interesting choice to do so would be to use 
Neurodocker~\cite{neurodocker}.
This tool traces and deletes unnecessary files.
However, it does not affect the number of installed packages.
Since image scanners report vulnerabilities according to the installed
packages. Therefore, after
minimization the same number of vulnerabilities is still reported.
Consequently, we need to reduce the number of installed packages
in the images by deleting unnecessary packages. For that, it is required to figure
out which packages we need for the pipeline to function properly. To allow for that, we utilize
Reprozip~\cite{rampin2016reprozip}, which is a tool that
is used to make applications reproducible \tristan{No it doesn't make applications reproducible}. This tool traces operating system calls used by the
application while execution, and then based on this trace, it recognizes binaries, files, environment variables,
and library dependencies that are used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, a list of packages that are needed for the application re-execution is determined. \tristan{How did you run the applications? Which command lines, why, etc} Following that, the list
is expanded by adding important and required packages that are essential
for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
~\cite{debtree} \tristan{does debtree work in centos? if not, how do you minimize centos images?}.
Effectively all needed packages are kept and remaining unnecessary packages are removed. We use
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
the image size reduction process \tristan{Can we please have at least a README for these scripts?}, which install Reprozip in the image, collect Reprozip trace, and
finally delete all unnecessary packages.

Following the above two approaches, we employ a hybrid approach, where
we combine both update and size reduction processes in an attempt to
lessen number of vulnerabilities or to test the effect of
combining two approaches. To allow for that, we first update all packages
the image, then delete all unnecessary packages. Applying these processes in reverse
may reduce the needed work; however this is not possible in all cases. For instance,
some packages, such as apt-transport-https, are required to fetch updates, deleting these packages
ahead of time will disallow the update process to take place.
%Finally, we combine both update and size reduction process
%to lessen the number of vulnerabilities.
%Therefore, in this process we first update all the packages in the image and then deletes
%the unnecessary packages. For this process we used the same scripts that
%we used for earlier experiments.
%\begin{comment}
%\subsection{CBRAIN}
%
%\href{http://github.com/aces/cbrain}{CBRAIN}~\cite{sherif2014cbrain} is a web portal that is
%used for the processing of distributed data on various storage locations of computing
%clusters. CBRAIN system deployed by Montreal Neurological Institute depends on the infrastructure
%delivered by Compute Canada~\cite{das2016mni}.
%It is also used by CONP to exploit services of Compute Canada. CBRAIN is a collaborative
%neuroimaging research platform that is active in production since 2009. CBRAIN
%provides transparent access to various distributed storage sites and computing
%resources across the world. CBRAIN’s infrastructure consists of three main
%layers, namely access layer, service layer, and infrastructure layer~\cite{sherif2014cbrain}. The access
%layer is for CBRAIN users, and can be accessed through any modern browser or
%RESTful API. The service layer consists of CBRAIN portal, which contains
%metadata and databases. It provides information about users, their permissions,
%resources etc. The infrastructure layer consists of data resources and computing
%resources, which are connected through a network. 
%CBRAIN supports Docker, Singularity, BIDS apps, and Boutiques.
%CBRAIN users uses a portal
%account on the cluster. Users are only able to
%run pre-defined applications on the cluster through the CBRAIN portal.
%\end{comment}
\section{Results}

@@

Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
the scanners and the overlap between them. \tristan{According to our discussion, this is only for Ubuntu. This should be clarified.}

>>>>

%%%%%%%%%Related Work%%%%%%%
The existing research work on containers focuses mainly on the security of containers.
This focus is justified by the fact that containers expose the host's resources
(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
threat for the applications running on the same host. Previous studies evaluated
the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis}.
Other work studied security vulnerabilities on Docker hub. A study in 2015 by Gummaraju et al.
states that over 30\% of official images in docker hub contain high priority 
security vulnerabilities~\cite{gummaraju2015over}. Shu et al. show that both official and community images 
contain more than 180 vulnerabilities on an average~\cite{Shu2017}.
Zerouali et al. studied that 
outdated packages lead to bugs and severity vulnerabilities in Docker
images~\cite{zerouali2019relation}.

@@

We scan a total of 44 container images taken from two containerization frameworks
used in neuroscience: BIDS
apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}.
Out of these 44 images, 26 were obtained from BIDS apps
(\url{https://bids-apps.neuroimaging.io/apps/}) 
and 18 from Boutiques. In fact, at the time of the study, BIDS apps had 27 images,
out of which one wasn't available on DockerHub. Boutiques had 49 images, listed using
Boutiques \texttt{bosh search} command,
however, only 23 unique images were listed, out of which 3 couldn't be retrieved and 2
were already included in BIDS apps. All the final 26 images
from BIDS apps are Docker images, whereas Boutiques contains 18 Docker images
and 6 Singularity images.

@@

Anchore is an end-to-end, open-source container security platform. It
analyses container images and lists OS
packages, non-OS packages (Python, Java, Gem, and Npm), and files.
In our experiments, we use Anchore Engine version 0.5.0 through Docker image \texttt{anchore/anchore-engine:v0.5.0}, and
Anchore vulnerability database version 0.0.11.

Anchore compares package versions, which are present inside the
image, with the vulnerability database in order to flag vulnerabilities.
To get a vulnerability feed of various OS distributions, Anchore refers to
different sources. The figure~\ref{anchore} displays a list of all sources
that it refers at the time of this study.

%for instance, Ubuntu launchpad database to get
%vulnerability data related to Ubuntu 
\tristan{You need to be accurate on these sources, this is not ``for instance". 
You should list all the sources used in the experiments, for all image types: Ubuntu but also CentOS, Debian, Alpine.}.

\begin{figure*}[!ht]
    \centering
	\begin{subfigure}[t]{0.3\textwidth}
        \includegraphics[height=2.0in]{Figures/anchore.png}
        \caption{Anchore}
        \label{anchore}
    \end{subfigure}%
    ~ 
	\begin{subfigure}[t]{0.3\textwidth}
        \includegraphics[height=2.5in]{Figures/vuls.png}
        \caption{Vuls}
        \label{vuls}
    \end{subfigure}
     ~
	\begin{subfigure}[t]{0.3\textwidth}
        \includegraphics[height=2.0in]{Figures/clair.png}
        \caption{Clair}
	\label{clair}
    \end{subfigure}
    \caption{Vulnerability databases used by scanners}
    \label{database}
\end{figure*}

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD. It
offers both static and dynamic scanning, and both local and remote
scanning. In our experiments, we use remote dynamic scanning, that is, Vuls
starts a container for every image to test, and queries the package manager
in the image through SSH. We use Vuls 0.9.0, executed through Docker image
\texttt{vuls/vuls:latest}. At the time of this study, Vuls gets vulnerability feed
from a configured set of sources, which are listed in Figure~\ref{vuls}.
%from the Open Vulnerability
%and Assessment Language (OVAL) database 
\tristan{Does it contain
vulnerabilities for all distributions?} 
\tristan{The Vuls website says that it uses multiple vulnerability databases: https://vuls.io/docs/en/main-features.html Are you sure 
that you only used OVAL and if so, why?}. According to this list, Vuls
refers to OVAL database for some distribution e.g. Ubuntu, Debian, etc.
It is worth noting that there is
no OVAL data for Ubuntu 17.04 and 17.10 distributions, meaning that images
with these distributions cannot be scanned with Vuls.

@@

Clair (\url{https://github.com/quay/clair}) is an open-source and extensible
vulnerability scanner for Docker and appc container images, developed by
CoreOS (now Container Linux), a Linux distribution to deploy container
clusters. Clair has a client-server architecture, in which the server
maintains a database of vulnerabilities. We use Clair through Clair scanner
(\url{https://github.com/arminc/clair-scanner}), a tool to facilitate the testing
of container images against a local Clair server. Clair scanner scans the image,
prepares the list of vulnerabilities, compares that list against a
whitelist, and flags vulnerabilities that are not present in the whitelist.
In our experiments, we did not use a whitelist to filter scanning results in
order to make a fair comparison between scanners.
\tristan{What is this whitelist about, and which one did you use?}. Clair
scanner maintains a Docker image with the up-to-date vulnerability
database from a set of different sources listed in Figure~\ref{clair}.  \tristan{Please mention the vulnerability sources for all distributions}.
 We use Clair-scanner version 2.0.6, executed through
Docker image \texttt{arminc/clair-local-scan:v2.0.6}. For the vulnerability
database, we use Docker image \texttt{arminc/clair-db:latest}, last
updated on 2019-09-18.

@@

Singularity Tools (Stools)
are an extension of Clair scanner for Singularity images. Stools
directly scan the image files in a local installation of the Clair
scanner, to circumvent the Docker-specific requirements in the Clair API.
In our experiments, we use Singularity Tools version 3.2.1 through Docker
image
\texttt{vanessa/stools-clair:v3.2.1}, which is using another Docker
image \texttt{arminc/clair-db:latest} for referring to vulnerability feed.
We follow the steps mentioned in
\href{https://github.com/singularityhub/stools}{Stools Github} to scan
Singularity images. \tristan{which docker images did you use for clair and clair database?}

@@

Ubuntu maintains its vulnerability database in the Ubuntu Launchpad or the Ubuntu CVE Tracker. For a given CVE, there is an entry for all ubuntu releases.
Ubuntu releases are listed with the package name
in which vulnerability exists and are entitled a status
(\url{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
encoded in the following form:
\newline \\
\noindent <release>\_<source-package>: <status> (<version/notes>) \\
\newline\\
For a given release, the status can be any one of the following:

@@

\subsection{Image Minimization Process}
We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
An interesting choice to do so would be to use 
Neurodocker~\cite{neurodocker}.
This tool traces and deletes unnecessary files.
However, it does not affect the number of installed packages.
Since image scanners report vulnerabilities according to the installed
packages. Therefore, after
minimization the same number of vulnerabilities is still reported.
Consequently, we need to reduce the number of installed packages
in the images by deleting unnecessary packages. For that, it is required to figure
out which packages we need for the pipeline to function properly. To allow for that, we utilize
Reprozip~\cite{rampin2016reprozip}, which is a tool that
is used to make applications reproducible \tristan{No it doesn't make applications reproducible}. This tool traces operating system calls used by the
application while execution, and then based on this trace, it recognizes binaries, files, environment variables,
and library dependencies that are used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, a list of packages that are needed for the application re-execution is determined. We run applications
using specific command lines given on application's Github repository in order to collect Reprozip trace.
These command lines represent how applications should be used.
\tristan{How did you run the applications? Which command lines, why, etc} Following that, the list
is expanded by adding important and required packages that are essential
for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
~\cite{debtree}, which is avaiable in Debian and Ubuntu. Its alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
gives a complete dependency tree.\tristan{does debtree work in centos? if not, how do you minimize centos images?}.
Effectively all needed packages are kept and remaining unnecessary packages are removed. We use
\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
the image size reduction process \tristan{Can we please have at least a README for these scripts?}, which install Reprozip in the image, collect Reprozip trace, and
finally delete all unnecessary packages.

Following the above two approaches, we employ a hybrid approach, where
we combine both update and size reduction processes in an attempt to
lessen number of vulnerabilities or to test the effect of
combining two approaches. To allow for that, we first update all packages
the image, then delete all unnecessary packages. Applying these processes in reverse
may reduce the needed work; however this is not possible in all cases. For instance,
some packages, such as \texttt{apt-transport-https}, are required to fetch updates, deleting these packages
ahead of time will disallow the update process to take place.
%Finally, we combine both update and size reduction process
%to lessen the number of vulnerabilities.
%Therefore, in this process we first update all the packages in the image and then deletes
%the unnecessary packages. For this process we used the same scripts that
%we used for earlier experiments.
%\begin{comment}
%\subsection{CBRAIN}
%
%\href{http://github.com/aces/cbrain}{CBRAIN}~\cite{sherif2014cbrain} is a web portal that is
%used for the processing of distributed data on various storage locations of computing
%clusters. CBRAIN system deployed by Montreal Neurological Institute depends on the infrastructure
%delivered by Compute Canada~\cite{das2016mni}.
%It is also used by CONP to exploit services of Compute Canada. CBRAIN is a collaborative
%neuroimaging research platform that is active in production since 2009. CBRAIN
%provides transparent access to various distributed storage sites and computing
%resources across the world. CBRAIN’s infrastructure consists of three main
%layers, namely access layer, service layer, and infrastructure layer~\cite{sherif2014cbrain}. The access
%layer is for CBRAIN users, and can be accessed through any modern browser or
%RESTful API. The service layer consists of CBRAIN portal, which contains
%metadata and databases. It provides information about users, their permissions,
%resources etc. The infrastructure layer consists of data resources and computing
%resources, which are connected through a network. 
%CBRAIN supports Docker, Singularity, BIDS apps, and Boutiques.
%CBRAIN users uses a portal
%account on the cluster. Users are only able to
%run pre-defined applications on the cluster through the CBRAIN portal.
%\end{comment}
\section{Results}

@@

Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
the scanners in Docker images and the overlap between them.
This figure excludes Centos Docker images because scanners report results in different
formats for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
to report pending patches that need to be applied to specific packages
,whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
vulnerabilities in packages. Also, we excluded two other images \texttt{bids/antscorticalthickness:v2.2.0-1} and
\texttt{bids/afni\_proc} from this figure, since we do not have Vuls scanning results for these images. 
\tristan{According to our discussion, this is only for Ubuntu. This should be clarified.}
